---
title: "Initial_Modelling_for_priors"
format: html
editor: 
  markdown: 
    wrap: 72
---
```{r}
#| message: false
#| warning: false
library(tidyverse)
library(DHARMa)
library(glmmTMB)
library(here)
library(splines)
library(MASS)
library(ggeffects)
library(car)
library(dotwhisker)
library(brms)
library(kingCoData)
library(ggmosaic)
library(GGally)
library(lme4)
library(performance)
library(lubridate)
```

## Data Sources
...



## Preprocessing and Exploration
```{r}

data(kingco_sales)
kingco_sales2016 <- kingco_sales |>
  dplyr::select(-c('pinx', 'sale_id', 'subdivision')) |>
  mutate(
    was_renod     = (year_reno > 0),
    has_bsmnt_gar = (garb_sqft > 0),
    has_att_gar   = (gara_sqft > 0),
    has_bsmt      = (sqft_fbsmt > 0),
    wfnt          = as.factor(wfnt > 0),
    year_sold     = year(ymd(sale_date))
  ) |> filter(year_sold > 2015) |> 
  slice_sample(n = 15000)

kingco_sales2016 <- kingco_sales2016 |> 
  mutate(
    sale_warning = na_if(sale_warning, "   ")
  ) |> 
  mutate(
    sale_warning = !is.na(sale_warning)
  )

kingco_sales <- NULL

```

```{r}
#| message: false

# Combine view columns into single binary
kingco_sales2016 |> 
  dplyr::select(starts_with('view_')) |> 
  pivot_longer(cols = everything(), values_to = 'View Indicator', names_to = 'View Type') |> 
  ggplot(mapping = aes(x = `View Indicator`)) + 
  geom_bar() + 
  facet_wrap(~ `View Type`)

kingco_sales2016 <- kingco_sales2016 |>
  mutate(view = rowSums(across(starts_with("view_"))) > 0) |>
  dplyr::select(-starts_with("view_"))

kingco_sales2016 |> 
  ggplot(mapping = aes(x = view)) +
  geom_bar()

# Drop unused join columns
kingco_sales2016 <- kingco_sales2016 |>
  dplyr::select(-c(join_year, join_status))
```

## Changing things to factors
```{r}
#| message: false

catagoricals <- c('sale_warning', 'area', 'city', 'zoning', 'golf', 'wfnt', 'greenbelt','present_use', 'noise_traffic', 'view', 'year_sold', 'stories', 'stories', 'was_renod', 'has_bsmnt_gar', 'has_att_gar', 'has_bsmt', 'condition')


kingco_sales2016 <- kingco_sales2016 |>
  mutate(across(all_of(catagoricals), as.factor))

kingco_sales2016 |>
  dplyr::select(all_of(catagoricals)) |>
  pivot_longer(everything(), names_to = "variable", values_to = "value") |>
  ggplot(aes(x = value)) +
  geom_bar() +
  facet_wrap(~ variable, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  xlab(NULL) + ylab("Count")


```

## Standardize Continuous Predictors
```{r}
#| message: false

kingco_sales2016 <- kingco_sales2016 |>
  mutate(across(where(is.numeric) & !sale_price, ~ as.numeric(scale(.x))))
```


## Prior Predictive Checking 

Suppose we are going to use 2 candidate priors. First, the 'weakly informative' priors given by brms. And the prior we elicited from our previously fitted model. 


```{r}
weak_prior <- c(
  prior(normal(0, 100), class = b),           # fixed effects (standardized predictors)
  prior(normal(0, 100), class = Intercept),   # intercept
  prior(exponential(0.1), class = sd),        # random effect SDs prior
  prior(exponential(0.1), class = sigma)
)
```


```{r}
#| eval: false
fit1 <- brms::brm(log(sale_price) ~
  # Structure of the House
  sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt +
  beds + bath_full + bath_3qtr + bath_half +
  stories +
  grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +

  # Time
  year_built + was_renod + year_reno +

  # Location features
  wfnt + golf + greenbelt + view +
  noise_traffic + longitude + latitude +

  # Transaction
  sale_warning + sale_nbr +

  # Random effects
  (1 | city) +
  (1 | area) +
  (1 | year_sold),

  data = kingco_sales2016,
  sample_prior = 'only', # IMPORTANT
  family = gaussian(),
  prior = weak_prior,
  chains = 4,
  cores = parallel::detectCores(),
  iter = 2000,
  warmup = 1000,
  seed = 123
)
```

```{r}
fit1 <- readRDS("~/Documents/Projects/BayesianWorkflow/prior_check_1.rds")
pp_check(fit1, prefix = 'ppd')
```

THESE PRIORS MAKE NO SENSE. Let's use what we learned from our previously fitted data. 


```{r}
#| eval: false
# # Build prior string for each coefficient
prior <- c(
  # Intercept
  prior(normal(13.07, 1.0), class = Intercept),

  # Structure
  prior(normal(0.14, 0.2),    class = b, coef = sqft),
  prior(normal(0.008, 0.1),   class = b, coef = sqft_lot),
  prior(normal(0.29, 0.2),    class = b, coef = sqft_1),
  prior(normal(0.02, 0.1),    class = b, coef = has_bsmtTRUE),
  prior(normal(-0.009, 0.1),  class = b, coef = sqft_fbsmt),
  prior(normal(-0.07, 0.1),   class = b, coef = beds),
  prior(normal(0.005, 0.1),   class = b, coef = bath_full),
  prior(normal(0.003, 0.1),   class = b, coef = bath_3qtr),
  prior(normal(0.0003, 0.1),  class = b, coef = bath_half),
  prior(normal(0.046, 0.2),   class = b, coef = stories1.5),
  prior(normal(0.059, 0.2),   class = b, coef = stories2),
  prior(normal(0.083, 0.2),   class = b, coef = stories2.5),
  prior(normal(0.051, 0.3),   class = b, coef = stories3),
  prior(normal(-0.076, 0.6),  class = b, coef = stories3.5),
  prior(normal(0.12, 0.1),    class = b, coef = grade),
  prior(normal(-0.147, 0.2),  class = b, coef = condition2),
  prior(normal(-0.221, 0.2),  class = b, coef = condition3),
  prior(normal(-0.230, 0.2),  class = b, coef = condition4),
  prior(normal(-0.242, 0.2),  class = b, coef = condition5),

  # Garage
  prior(normal(0.037, 0.1),   class = b, coef = gara_sqft),
  prior(normal(-0.003, 0.1),  class = b, coef = has_att_garTRUE),
  prior(normal(-0.008, 0.1),  class = b, coef = garb_sqft),
  prior(normal(0.041, 0.1),   class = b, coef = has_bsmnt_garTRUE),

  # Time
  prior(normal(-0.060, 0.1),  class = b, coef = year_built),
  prior(normal(-2.80, 4.0),   class = b, coef = was_renodTRUE),
  prior(normal(0.447, 0.6),   class = b, coef = year_reno),

  # Location
  prior(normal(0.358, 0.4),   class = b, coef = wfntTRUE),
  prior(normal(0.109, 0.2),   class = b, coef = golf1),
  prior(normal(0.054, 0.1),   class = b, coef = greenbelt1),
  prior(normal(0.137, 0.1),   class = b, coef = viewTRUE),
  prior(normal(-0.026, 0.1),  class = b, coef = noise_traffic1),
  prior(normal(-0.058, 0.1),  class = b, coef = noise_traffic2),
  prior(normal(-0.071, 0.1),  class = b, coef = noise_traffic3),
  prior(normal(-0.056, 0.1),  class = b, coef = longitude),
  prior(normal(0.071, 0.1),   class = b, coef = latitude),

  # Transaction
  prior(normal(-0.121, 0.1),  class = b, coef = sale_warningTRUE),
  prior(normal(0.030, 0.1),   class = b, coef = sale_nbr),

  # Random effect SDs
  prior(normal(0.20, 0.2),    class = sd, group = area),
  prior(normal(0.05, 0.1),    class = sd, group = city),
  prior(normal(0.21, 0.2),    class = sd, group = year_sold),

  # Residual
  prior(normal(0.22, 0.2),    class = sigma)
)



fit2 <- brms::brm(log(sale_price) ~
  # Structure of the House
  sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt +
  beds + bath_full + bath_3qtr + bath_half +
  stories +
  grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +

  # Time
  year_built + was_renod + year_reno +

  # Location features
  wfnt + golf + greenbelt + view +
  noise_traffic + longitude + latitude +

  # Transaction
  sale_warning + sale_nbr +

  # Random effects
  (1 | city) +
  (1 | area) +
  (1 | year_sold),

  data = kingco_sales2016,
  prior = prior,
  family = gaussian(),
  chains = 4,
  cores = parallel::detectCores(),
  sample_prior = 'only',
  iter = 2000,
  warmup = 1000,
  seed = 123
)

# a little too low, increasing the intercept;

```


Doing a prior predictive check:
```{r}
fit2 <- readRDS("~/Documents/Projects/BayesianWorkflow/prior_check_2.rds")
pp_check(fit2, prefix = 'ppd')

```

```{r}
#| eval: false
# Build prior string for each coefficient

prior <- c(
  # Intercept
  prior(normal(15, 1.0), class = Intercept),

  # Structure
  prior(normal(0.14, 0.2),    class = b, coef = sqft),
  prior(normal(0.008, 0.1),   class = b, coef = sqft_lot),
  prior(normal(0.29, 0.2),    class = b, coef = sqft_1),
  prior(normal(0.02, 0.1),    class = b, coef = has_bsmtTRUE),
  prior(normal(-0.009, 0.1),  class = b, coef = sqft_fbsmt),
  prior(normal(-0.07, 0.1),   class = b, coef = beds),
  prior(normal(0.005, 0.1),   class = b, coef = bath_full),
  prior(normal(0.003, 0.1),   class = b, coef = bath_3qtr),
  prior(normal(0.0003, 0.1),  class = b, coef = bath_half),
  prior(normal(0.046, 0.2),   class = b, coef = stories1.5),
  prior(normal(0.059, 0.2),   class = b, coef = stories2),
  prior(normal(0.083, 0.2),   class = b, coef = stories2.5),
  prior(normal(0.051, 0.3),   class = b, coef = stories3),
  prior(normal(-0.076, 0.6),  class = b, coef = stories3.5),
  prior(normal(0.12, 0.1),    class = b, coef = grade),
  prior(normal(-0.147, 0.2),  class = b, coef = condition2),
  prior(normal(-0.221, 0.2),  class = b, coef = condition3),
  prior(normal(-0.230, 0.2),  class = b, coef = condition4),
  prior(normal(-0.242, 0.2),  class = b, coef = condition5),

  # Garage
  prior(normal(0.037, 0.1),   class = b, coef = gara_sqft),
  prior(normal(-0.003, 0.1),  class = b, coef = has_att_garTRUE),
  prior(normal(-0.008, 0.1),  class = b, coef = garb_sqft),
  prior(normal(0.041, 0.1),   class = b, coef = has_bsmnt_garTRUE),

  # Time
  prior(normal(-0.060, 0.1),  class = b, coef = year_built),
  prior(normal(-2.80, 4.0),   class = b, coef = was_renodTRUE),
  prior(normal(0.447, 0.6),   class = b, coef = year_reno),

  # Location
  prior(normal(0.358, 0.4),   class = b, coef = wfntTRUE),
  prior(normal(0.109, 0.2),   class = b, coef = golf1),
  prior(normal(0.054, 0.1),   class = b, coef = greenbelt1),
  prior(normal(0.137, 0.1),   class = b, coef = viewTRUE),
  prior(normal(-0.026, 0.1),  class = b, coef = noise_traffic1),
  prior(normal(-0.058, 0.1),  class = b, coef = noise_traffic2),
  prior(normal(-0.071, 0.1),  class = b, coef = noise_traffic3),
  prior(normal(-0.056, 0.1),  class = b, coef = longitude),
  prior(normal(0.071, 0.1),   class = b, coef = latitude),

  # Transaction
  prior(normal(-0.121, 0.1),  class = b, coef = sale_warningTRUE),
  prior(normal(0.030, 0.1),   class = b, coef = sale_nbr),

  # Random effect SDs
  prior(normal(0.20, 0.2),    class = sd, group = area),
  prior(normal(0.05, 0.1),    class = sd, group = city),
  prior(normal(0.21, 0.2),    class = sd, group = year_sold),

  # Residual
  prior(normal(0.22, 0.2),    class = sigma)
)



fit3 <- brms::brm(log(sale_price) ~
  # Structure of the House
  sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt +
  beds + bath_full + bath_3qtr + bath_half +
  stories +
  grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +

  # Time
  year_built + was_renod + year_reno +

  # Location features
  wfnt + golf + greenbelt + view +
  noise_traffic + longitude + latitude +

  # Transaction
  sale_warning + sale_nbr +

  # Random effects
  (1 | city) +
  (1 | area) +
  (1 | year_sold),

  data = kingco_sales2016,
  prior = prior,
  family = gaussian(),
  chains = 4,
  cores = parallel::detectCores(),
  sample_prior = 'only',
  iter = 2000,
  warmup = 1000,
  seed = 123
)



```

Doing a prior preditve check:
```{r}

fit3 <- readRDS("~/Documents/Projects/BayesianWorkflow/prior_check_3.rds")
pp_check(fit3, prefix = 'ppd', ndraws = 100)

```


Given where we got our prior from, this makes sense. 

## Fitting the model

Try fitting our model:
```{r}
#| eval: false


# Build prior string for each coefficient

prior <- c(
  # Intercept
  prior(normal(15, 1.0), class = Intercept),

  # Structure
  prior(normal(0.14, 0.2),    class = b, coef = sqft),
  prior(normal(0.008, 0.1),   class = b, coef = sqft_lot),
  prior(normal(0.29, 0.2),    class = b, coef = sqft_1),
  prior(normal(0.02, 0.1),    class = b, coef = has_bsmtTRUE),
  prior(normal(-0.009, 0.1),  class = b, coef = sqft_fbsmt),
  prior(normal(-0.07, 0.1),   class = b, coef = beds),
  prior(normal(0.005, 0.1),   class = b, coef = bath_full),
  prior(normal(0.003, 0.1),   class = b, coef = bath_3qtr),
  prior(normal(0.0003, 0.1),  class = b, coef = bath_half),
  prior(normal(0.046, 0.2),   class = b, coef = stories1.5),
  prior(normal(0.059, 0.2),   class = b, coef = stories2),
  prior(normal(0.083, 0.2),   class = b, coef = stories2.5),
  prior(normal(0.051, 0.3),   class = b, coef = stories3),
  prior(normal(-0.076, 0.6),  class = b, coef = stories3.5),
  prior(normal(0.12, 0.1),    class = b, coef = grade),
  prior(normal(-0.147, 0.2),  class = b, coef = condition2),
  prior(normal(-0.221, 0.2),  class = b, coef = condition3),
  prior(normal(-0.230, 0.2),  class = b, coef = condition4),
  prior(normal(-0.242, 0.2),  class = b, coef = condition5),

  # Garage
  prior(normal(0.037, 0.1),   class = b, coef = gara_sqft),
  prior(normal(-0.003, 0.1),  class = b, coef = has_att_garTRUE),
  prior(normal(-0.008, 0.1),  class = b, coef = garb_sqft),
  prior(normal(0.041, 0.1),   class = b, coef = has_bsmnt_garTRUE),

  # Time
  prior(normal(-0.060, 0.1),  class = b, coef = year_built),
  prior(normal(-2.80, 4.0),   class = b, coef = was_renodTRUE),
  prior(normal(0.447, 0.6),   class = b, coef = year_reno),

  # Location
  prior(normal(0.358, 0.4),   class = b, coef = wfntTRUE),
  prior(normal(0.109, 0.2),   class = b, coef = golf1),
  prior(normal(0.054, 0.1),   class = b, coef = greenbelt1),
  prior(normal(0.137, 0.1),   class = b, coef = viewTRUE),
  prior(normal(-0.026, 0.1),  class = b, coef = noise_traffic1),
  prior(normal(-0.058, 0.1),  class = b, coef = noise_traffic2),
  prior(normal(-0.071, 0.1),  class = b, coef = noise_traffic3),
  prior(normal(-0.056, 0.1),  class = b, coef = longitude),
  prior(normal(0.071, 0.1),   class = b, coef = latitude),

  # Transaction
  prior(normal(-0.121, 0.1),  class = b, coef = sale_warningTRUE),
  prior(normal(0.030, 0.1),   class = b, coef = sale_nbr),

  # Random effect SDs
  prior(normal(0.20, 0.2),    class = sd, group = area),
  prior(normal(0.05, 0.1),    class = sd, group = city),
  prior(normal(0.21, 0.2),    class = sd, group = year_sold),

  # Residual
  prior(normal(0.22, 0.2),    class = sigma)
)



fit3 <- brms::brm(log(sale_price) ~
  # Structure of the House
  sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt +
  beds + bath_full + bath_3qtr + bath_half +
  stories +
  grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +

  # Time
  year_built + was_renod + year_reno +

  # Location features
  wfnt + golf + greenbelt + view +
  noise_traffic + longitude + latitude +

  # Transaction
  sale_warning + sale_nbr +

  # Random effects
  (1 | city) +
  (1 | area) +
  (1 | year_sold),

  data = kingco_sales2016,
  prior = prior,
  family = gaussian(),
  chains = 4,
  cores = parallel::detectCores(),
  iter = 2000,
  warmup = 1000,
  seed = 123
)




```

Our model failed to converge (took too long to run.)

Try weaker priors; you should check the prior predictive distribution again:

```{r}
#| eval: false
#Build prior string for each coefficient

prior <- c(
  # Intercept
 prior(normal(15, 2.0), class = Intercept),
 # Structure
 prior(normal(0.14, 2),    class = b, coef = sqft),
 prior(normal(0.008, 1),   class = b, coef = sqft_lot),
 prior(normal(0.29, 2),    class = b, coef = sqft_1),
 prior(normal(0.02, 1),    class = b, coef = has_bsmtTRUE),
 prior(normal(-0.009, 1),  class = b, coef = sqft_fbsmt),
 prior(normal(-0.07, 1),   class = b, coef = beds),
 prior(normal(0.005, 1),   class = b, coef = bath_full),
 prior(normal(0.003, 1),   class = b, coef = bath_3qtr),
 prior(normal(0.0003, 1),  class = b, coef = bath_half),
 prior(normal(0.046, 2),   class = b, coef = stories1.5),
 prior(normal(0.059, 2),   class = b, coef = stories2),
 prior(normal(0.083, 2),   class = b, coef = stories2.5),
 prior(normal(0.051, 3),   class = b, coef = stories3),
 prior(normal(-0.076, 6),  class = b, coef = stories3.5),
 prior(normal(0.12, 1),    class = b, coef = grade),
 prior(normal(-0.147, 2),  class = b, coef = condition2),
 prior(normal(-0.221, 2),  class = b, coef = condition3),
 prior(normal(-0.230, 2),  class = b, coef = condition4),
 prior(normal(-0.242, 2),  class = b, coef = condition5),
#   # Garage
 prior(normal(0.037, 1),   class = b, coef = gara_sqft),
 prior(normal(-0.003, 1),  class = b, coef = has_att_garTRUE),
 prior(normal(-0.008, 1),  class = b, coef = garb_sqft),
 prior(normal(0.041, 1),   class = b, coef = has_bsmnt_garTRUE),
#   # Time
 prior(normal(-0.060, 1),  class = b, coef = year_built),
 prior(normal(-2.80, 4.0),   class = b, coef = was_renodTRUE),
 prior(normal(0.447, 6),   class = b, coef = year_reno),
#   # Location
 prior(normal(0.358, 4),   class = b, coef = wfntTRUE),
 prior(normal(0.109, 2),   class = b, coef = golf1),
 prior(normal(0.054, 1),   class = b, coef = greenbelt1),
 prior(normal(0.137, 1),   class = b, coef = viewTRUE),
 prior(normal(-0.026, 1),  class = b, coef = noise_traffic1),
 prior(normal(-0.058, 1),  class = b, coef = noise_traffic2),
 prior(normal(-0.071, 1),  class = b, coef = noise_traffic3),
 prior(normal(-0.056, 1),  class = b, coef = longitude),
 prior(normal(0.071, 1),   class = b, coef = latitude),
#   # Transaction
 prior(normal(-0.121, 1),  class = b, coef = sale_warningTRUE),
 prior(normal(0.030, 1),   class = b, coef = sale_nbr),
#   # Random effect SDs
 prior(normal(0.20, 2),    class = sd, group = area),
 prior(normal(0.05, 1),    class = sd, group = city),
 prior(normal(0.21, 2),    class = sd, group = year_sold),
#   # Residual
 prior(normal(0.22, 2),    class = sigma)
)
#
#
#
fit4_mcmc <- brms::brm(log(sale_price) ~
 # Structure of the House
sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt +
beds + bath_full + bath_3qtr + bath_half +
 stories +
 grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +
#   # Time
 year_built + was_renod + year_reno +
#   # Location features
 wfnt + golf + greenbelt + view +
 noise_traffic + longitude + latitude +
#   # Transaction
 sale_warning + sale_nbr +
#   # Random effects
 (1 | city) +
 (1 | area) +
 (1 | year_sold),
 data = kingco_sales2016,
 prior = prior,
 family = gaussian(),
 seed = 123,
 sample_prior = 'only', 
 algorithm = 'sampling'
)



```
I got multple warnings here:

Warning :The largest R-hat is 2.17, indicating chains have not mixed.
Warning :Bulk Effective Samples Size (ESS) is too low, indicating posterior means and medians may be unreliable.
Warning :Tail Effective Samples Size (ESS) is too low, indicating posterior variances and tail quantiles may be unreliable.


### let's check the Trace plots to assess convergence

```{r}
fit4_mcmc <- readRDS("~/Documents/Projects/BayesianWorkflow/prior_check_4.rds")
plot(fit4_mcmc)

```


#### Posterior Predictive distribution is also non-sense
```{r}

pp_check(fit4_mcmc, prefix = 'ppd')

```


Let's try using a different algorithm to fit our original model:

```{r}
#| eval: false

# Build prior string for each coefficient

prior <- c(
  # Intercept
  prior(normal(15, 1.0), class = Intercept),

  # Structure
  prior(normal(0.14, 0.2),    class = b, coef = sqft),
  prior(normal(0.008, 0.1),   class = b, coef = sqft_lot),
  prior(normal(0.29, 0.2),    class = b, coef = sqft_1),
  prior(normal(0.02, 0.1),    class = b, coef = has_bsmtTRUE),
  prior(normal(-0.009, 0.1),  class = b, coef = sqft_fbsmt),
  prior(normal(-0.07, 0.1),   class = b, coef = beds),
  prior(normal(0.005, 0.1),   class = b, coef = bath_full),
  prior(normal(0.003, 0.1),   class = b, coef = bath_3qtr),
  prior(normal(0.0003, 0.1),  class = b, coef = bath_half),
  prior(normal(0.046, 0.2),   class = b, coef = stories1.5),
  prior(normal(0.059, 0.2),   class = b, coef = stories2),
  prior(normal(0.083, 0.2),   class = b, coef = stories2.5),
  prior(normal(0.051, 0.3),   class = b, coef = stories3),
  prior(normal(-0.076, 0.6),  class = b, coef = stories3.5),
  prior(normal(0.12, 0.1),    class = b, coef = grade),
  prior(normal(-0.147, 0.2),  class = b, coef = condition2),
  prior(normal(-0.221, 0.2),  class = b, coef = condition3),
  prior(normal(-0.230, 0.2),  class = b, coef = condition4),
  prior(normal(-0.242, 0.2),  class = b, coef = condition5),

  # Garage
  prior(normal(0.037, 0.1),   class = b, coef = gara_sqft),
  prior(normal(-0.003, 0.1),  class = b, coef = has_att_garTRUE),
  prior(normal(-0.008, 0.1),  class = b, coef = garb_sqft),
  prior(normal(0.041, 0.1),   class = b, coef = has_bsmnt_garTRUE),

  # Time
  prior(normal(-0.060, 0.1),  class = b, coef = year_built),
  prior(normal(-2.80, 4.0),   class = b, coef = was_renodTRUE),
  prior(normal(0.447, 0.6),   class = b, coef = year_reno),

  # Location
  prior(normal(0.358, 0.4),   class = b, coef = wfntTRUE),
  prior(normal(0.109, 0.2),   class = b, coef = golf1),
  prior(normal(0.054, 0.1),   class = b, coef = greenbelt1),
  prior(normal(0.137, 0.1),   class = b, coef = viewTRUE),
  prior(normal(-0.026, 0.1),  class = b, coef = noise_traffic1),
  prior(normal(-0.058, 0.1),  class = b, coef = noise_traffic2),
  prior(normal(-0.071, 0.1),  class = b, coef = noise_traffic3),
  prior(normal(-0.056, 0.1),  class = b, coef = longitude),
  prior(normal(0.071, 0.1),   class = b, coef = latitude),

  # Transaction
  prior(normal(-0.121, 0.1),  class = b, coef = sale_warningTRUE),
  prior(normal(0.030, 0.1),   class = b, coef = sale_nbr),

  # Random effect SDs
  prior(normal(0.20, 0.2),    class = sd, group = area),
  prior(normal(0.05, 0.1),    class = sd, group = city),
  prior(normal(0.21, 0.2),    class = sd, group = year_sold),

  # Residual
  prior(normal(0.22, 0.2),    class = sigma)
)



fit3_vi <- brms::brm(log(sale_price) ~
  # Structure of the House
  sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt +
  beds + bath_full + bath_3qtr + bath_half +
  stories +
  grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +

  # Time
  year_built + was_renod + year_reno +

  # Location features
  wfnt + golf + greenbelt + view +
  noise_traffic + longitude + latitude +

  # Transaction
  sale_warning + sale_nbr +

  # Random effects
  (1 | city) +
  (1 | area) +
  (1 | year_sold),

  data = kingco_sales2016,
  prior = prior,
  family = gaussian(),
  algorithm = 'meanfield', # use variational inference.
  seed = 123
)


```


```{r}
fit3_vi <- readRDS("~/Documents/Projects/BayesianWorkflow/fit3_vi.rds")
pp_check(fit3_vi, ndraws = 100)

```

```{r}
# Plot results
library(tidybayes)

mcmc_plot(fit3_vi, type = "intervals")   # posterior intervals

```




```{r}


fit3_vi %>%
  gather_draws(b_wfntTRUE, b_grade, b_was_renodTRUE,b_sqft, b_longitude, b_latitude, b_sale_warningTRUE) %>%
  ggplot(aes(x = .value, y = .variable)) +
  stat_halfeye() +
  theme_minimal() + 
  xlab('Value') + 
  ylab('Variable')

```

The fact that it was renod