---
title: "Initial_Modelling_for_priors"
format: html
editor: 
  markdown: 
    wrap: 72
---
```{r}
#| message: false
#| warning: false
library(tidyverse)
library(DHARMa)
library(glmmTMB)
library(here)
library(splines)
library(MASS)
library(ggeffects)
library(car)
library(dotwhisker)
library(brms)
library(kingCoData)
library(ggmosaic)
library(GGally)
library(lme4)
library(performance)
library(lubridate)
```

## Data Sources
...



## Preprocessing and Exploration

First thing to watch out for is how missing data is treated. 

```{r}
data(kingco_sales)


kingco_sales <- kingco_sales |>
  dplyr::select(-c(pinx, sale_id, subdivision)) |>
  mutate(
    was_renod     = (year_reno > 0),
    has_bsmnt_gar = (garb_sqft > 0),
    has_att_gar   = (gara_sqft > 0),
    has_bsmt      = (sqft_fbsmt > 0),
    wfnt          = as.factor(wfnt > 0),
    year_sold     = year(ymd(sale_date))
  )

kingco_sales2015 <- kingco_sales |>
  filter(year_sold <= 2015) |> 
  slice_sample(n = 15000)

kingco_sales2015 <- kingco_sales2015 |> 
  mutate(
    sale_warning = na_if(sale_warning, "   ")
  ) |> 
  mutate(
    sale_warning = !is.na(sale_warning)
  )

```


## Catagorical Variables


When including categorical variables, you need to ask whether or not there is enough data to estimate the effects of different catagories. 

```{r}
#| message: false

# Combine view columns into single binary
kingco_sales2015 |> 
  dplyr::select(starts_with('view_')) |> 
  pivot_longer(cols = everything(), values_to = 'View Indicator', names_to = 'View Type') |> 
  ggplot(mapping = aes(x = `View Indicator`)) + 
  geom_bar() + 
  facet_wrap(~ `View Type`)

kingco_sales2015 <- kingco_sales2015 |>
  mutate(view = rowSums(across(starts_with("view_"))) > 0) |>
  dplyr::select(-starts_with("view_"))

kingco_sales2015 |> 
  ggplot(mapping = aes(x = view)) +
  geom_bar()

# Drop unused join columns
kingco_sales2015 <- kingco_sales2015 |>
  dplyr::select(-c(join_year, join_status))
```

2 types: nominal, and ordinal


Just because it is not continuous, doesn't mean you shouldn't treat it as such. 

```{r}

kingco_sales2015 |> ggplot(aes(x = grade)) +
  geom_bar()

```

When treating ordinal data as continuous, how have to ask whether there are enough catagories.

## Changing things to factors
```{r}
#| message: false

catagoricals <- c('sale_warning', 'area', 'city', 'zoning', 'golf', 'wfnt', 'greenbelt','present_use', 'noise_traffic', 'view', 'year_sold', 'stories', 'stories', 'was_renod', 'has_bsmnt_gar', 'has_att_gar', 'has_bsmt', 'condition')


kingco_sales2015 <- kingco_sales2015 |>
  mutate(across(all_of(catagoricals), as.factor))

kingco_sales2015 |>
  dplyr::select(all_of(catagoricals)) |>
  pivot_longer(everything(), names_to = "variable", values_to = "value") |>
  ggplot(aes(x = value)) +
  geom_bar() +
  facet_wrap(~ variable, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  xlab(NULL) + ylab("Count")


kingco_sales2015 |> 
  ggplot(aes(x = condition)) + geom_bar()
```

## Standardize Continuous Predictors
```{r}
#| message: false

kingco_sales2015 <- kingco_sales2015 |>
  mutate(across(where(is.numeric) & !sale_price, ~ as.numeric(scale(.x))))
```


## EDA
```{r}
#| message: false

# Sale year distribution

# Categorical pairs (excluding high-cardinality grouping vars)
#kingco_sales2015 |>
#  dplyr::select(all_of(categoricals)) |>
#  dplyr::select(-c(area, city, zoning)) |>
#  GGally::ggpairs(cardinality_threshold = 20)

# Continuous pairs (split into chunks)
#kingco_sales2015 |>
#  dplyr::select(where(is.numeric) & !sale_price) |>
#  GGally::ggpairs(columns = 2:6)

#kingco_sales2015 |>
#  dplyr::select(where(is.numeric) & !sale_price) |>
#  GGally::ggpairs(columns = 7:15)

#kingco_sales2015 |>
#  dplyr::select(where(is.numeric) & !sale_price) |>
#  GGally::ggpairs(columns = 16:21)
```

## Model
```{r}

fit1 <- lme4::lmer(sale_price ~
   # Structure of the House
   sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt + 
   beds + bath_full + bath_3qtr + bath_half +
   stories +
   grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +
   
   # Time 
   year_built +  was_renod + year_reno  +
   
   
   # Location features
   wfnt + golf + greenbelt + view +
   noise_traffic + longitude + latitude +
   
   # Transaction
   sale_warning + sale_nbr +
   
   # Random effects
   (1 | city) +     # city nested in area
   (1 | area) + 
   (1 | year_sold),
  data = kingco_sales2015
)

```

## Model Diagnostics
```{r}
performance::check_model(fit1)
```

## Fixing the homogeneity of variance assumption
```{r}

fit1 <- lme4::lmer(log(sale_price) ~
   # Structure of the House
   sqft + sqft_lot + sqft_1 + has_bsmt + sqft_fbsmt + 
   beds + bath_full + bath_3qtr + bath_half +
   stories +
   grade + condition + gara_sqft + has_att_gar + garb_sqft + has_bsmnt_gar +
   
   # Time 
   year_built +  was_renod + year_reno  +
   
   
   # Location features
   wfnt + golf + greenbelt + view +
   noise_traffic + longitude + latitude +
   
   # Transaction
   sale_warning + sale_nbr +
   
   # Random effects
   (1 | city) +     # city nested in area
   (1 | area) + 
   (1 | year_sold),
  data = kingco_sales2015
)

saveRDS(fit1, 'priorfit2.rds')
```

## Model Diagnostics
```{r}
performance::check_model(fit1)

```