---
title: "Initial_Modelling_for_priors"
format: html
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(DHARMa)
library(glmmTMB)
library(here)
library(splines)
library(MASS)
library(ggeffects)
library(car)
library(dotwhisker)
library(brms)
library(kingCoData)
library(ggmosaic)
```

## Data Sources

The data were used for this analysis is from a few different sources.
The first source was
[kaggle](https://www.kaggle.com/datasets/open-source-sports/professional-hockey-database?select=Master.csv),
which sites *open source sports* as being the primary source of the
data. This site was used to gather data on when players played their
last game, and which team did they spend the majority of their careers.
The second source for this data set is
[QuantHockey](https://www.quanthockey.com/). This site was used to
gather data on the number of Stanley Cup final games played by the top
1000 players with the most Stanley cup finals games. Finally, data for
playoff goals per game, playoff assists per game, playoff penalty
minutes per game, and playoff plus minus per game, was sourced from [NHL
Official Site](https://www.nhl.com/). This data was used to estimate
player performance. None of the sites offer a description about any
intended research to be performed on the data sets they provide.

## Description

-   `sale_id`: The unique transaction identifying code.

-    `pinx`: The unique property identifying code (Major + Minor). Original
value is preceded by two '..'s to prevent the dropping of leading zeros

-    `sale_date`: Date of sale

-    `sale_price`: Price of the home

-    `sale_nbr`: Count of times this property sold during time period

-     `sale_warning`: Assessor's warning code for this sale

-    `join_status`: Type of data join, see 'explain("join_status") for more details

-    `join_year`: Year of data joined to the sale – based on 'join_status'

-    `longitude`: Longitude

-    `latitude`: Latitude

-    `area`: Assessment area or zone

-    `city`: City

-    `zoning`: Local zoning code

-     `present_use`: Property Use Code

-    `land_val`: Land Tax Value (based on Join Year)

-    `imp_val`: Improved Tax Value (based on Join Year)

-    `year_built`: Year home built

-    `year_reno`: Year major renovation

-    `sqft_lot`: Lot size in square feet

-    `sqft`: Square footage of house

-    `sqft_1`: Square footage of first floor

-     `sqft_fbsmt`: Square footage of finished basement

-    `grade`: Building quality

-    `fbsmt_grade`: Building quality of finished basement

-    `condition`: Home condition

-    `stories`: \# of Stories

-    `beds`: \# of beds

-    `bath_full`: \# of Full Baths

-     `bath_3qtr`: \# of 3/4 Baths

-    `bath_half`: \# of 1/2 Baths

-    `garb_sqft`: Basement garage square feet

-    `gara_sqft`: Attached garage square feetn

-    `wfnt`: Waterfront rating

-    `golf`: On golf course

-    `greenbelt`: On greenbelt

-    `traffic_noies`: Traffic Noise rating

-    `view_rainier`: View of Mt. Raininer

-    `view_olympics`: View of Olympic Mountains

-    `view_cascades`: View of Cascade Mountains

-    `view_territorial`: Territorial View

-    `view_skyline`: View of Seattle Skyline

-    `view_sound`: View of Puget Sound

-    `view_lakewash`: View of Lake Washington

-    `view_lakesamm`: View of Lake Sammammish

-    `view_otherwater`: View of Other Water

-    `view_other`: View of Other

-    `submarket`: 'Area' Field grouped into larger submarkets (subjective)


```{r}
# First, we are going to split the data, and then we are going to combine the view things into a single factor. We should also look at some histograms of the data. 

# Distribution of the catagorical variables
data(kingco_sales)
kingco_sales <- kingco_sales %>% dplyr::mutate(
  year_sold = year(lubridate::ymd(sale_date))
) 
kingco_sales2015 <- kingco_sales %>% filter(
  year_sold <= 2015
)
kingco_sales2015 %>% ggplot2::ggplot(aes(x = year_sold)) + 
  geom_bar(width = 0.5) +
  theme_minimal() + 
  scale_x_continuous(breaks = kingco_sales2015$year_sold) + 
  xlab('Sale Year') + 
  ylab('Count')

```
```{r}
# now looking at area. 
kingco_sales2015 %>% group_by(area) %>% summarise(
    count = n()
  ) %>% pull(count) %>% min()
kingco_sales2015 %>% ggplot2::ggplot(aes(x = area)) + 
  geom_bar(width = 0.5) +
  theme_minimal() + 
  xlab('Area') + 
  ylab('Count')


```

```{r}
# I'm gonna also provisionally look at city, and zoning too
kingco_sales2015 %>% group_by(city) %>% summarise(
    count = n()
  ) %>% pull(count) %>% min()
kingco_sales2015 %>% ggplot2::ggplot(aes(x = city)) + 
  geom_bar(width = 0.5) +
  theme_minimal() + 
  xlab('City') + 
  ylab('Count') + 
  theme(axis.text.x = element_text(angle = 45, size = 8, hjust = 1))

```

The potential (random effects) I have in mind are:

sale_date,
area,
city,
zoning,


```{r}
kingco_sales2015 %>% group_by(zoning) %>% summarise(
    count = n()
  ) %>% pull(count) %>% min()
kingco_sales2015 %>% group_by(zoning) %>%filter(n() > 500) %>% ungroup() %>% ggplot2::ggplot(aes(x = zoning)) + 
  geom_bar(width = 0.5) +
  theme_minimal() + 
  xlab('Zone') + 
  ylab('Count') + 
  theme(axis.text.x = element_text(angle = 90, size = 7, hjust = 1))


```


Based on the preliminary analysis, it might be reasonable to include zoning, area, city, and year. Gonna do some follow up plots to see if there is enough 

```{r}
kingco_sales2015 %>% group_by(zoning) %>% summarise(
    count = n()
  ) %>% pull(count) %>% min()
kingco_sales2015 %>% ggplot2::ggplot(aes(x = zoning)) + 
  geom_bar(width = 0.5) +
  theme_minimal() + 
  xlab('City') + 
  ylab('Count') + 
  theme(axis.text.x = element_text(angle = 90, size = 5, hjust = 1))

```


```{r}
options(scipen = 999)
kingco_sales2015 %>%
  dplyr::select(starts_with("view_")) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable)
kingco_sales2015 = kingco_sales2015 %>% mutate(view = rowSums(across(starts_with("view_"))) > 0)

```

```{r}
# a little better now
kingco_sales2015 %>% ggplot(aes(x = view)) +
  geom_bar()

```


```{r}
# removing view_ stuff
kingco_sales2015 <- kingco_sales %>% dplyr::select(
  -starts_with('view_')
)

# doing the same with baths:

kingco_sales2015 |> 
  dplyr::select(starts_with('bath_')) |> 
  pivot_longer(cols = everything(), names_to = 'BathType', values_to = 'bath_count') |> 
  ggplot(mapping = aes(x = bath_count)) +
  geom_bar() +
  facet_wrap(~BathType)

kingco_sales2015 |> 
  group_by(bath_full) |> 
  summarise(
    count = n(),
    pct = n() / nrow(kingco_sales2015) * 100) |> 
  ggplot(mapping = aes(x = bath_full, y = pct)) + 
  geom_line() +
  geom_point
kingco_sales2015 |> 
  group_by(bath_3qtr) |> 
  summarise(count = n(),
            pct = n() / nrow(kingco_sales2015) * 100)
kingco_sales2015 |> 
  group_by(bath_half) |> 
  summarise(count = n(),
            pct = n() / nrow(kingco_sales2015) * 100)
```




